Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2016-08-14 paper/figures.tex
Move internal resources CDF legend to above figure

\tikzsetnextfilename{mini-1x1-internal-resources-cdf}
\begin{tikzpicture}
\begin{axis}[
	% title=(a) Internal resources,
	datasetsCDF,
	datasetsCDFMiniResults,
	paperTight,
	xlabel=Ratio of internal resources,
	ylabel=Ratio of domains,
	legend style={at={(1.03,.5)}, anchor=west},
	xlabel style={
		at={(0.5,0.1)}
	},
	ylabel style={
		at={(0.17,0.5)}
	},
]

@@

>>>>

\tikzsetnextfilename{mini-1x1-internal-resources-cdf}
\begin{tikzpicture}
\begin{axis}[
	% title=(a) Internal resources,
	datasetsCDF,
	datasetsCDFMiniResults,
	paperTight,
	xlabel=Ratio of internal resources,
	ylabel=Ratio of domains,
	legend columns=2,
	legend style={at={(0.5,1.04)}, anchor=south},
	xlabel style={
		at={(0.5,0.1)}
	},
	ylabel style={
		at={(0.17,0.5)}
	},
]

@@

	\legend{Top 10k global,HTTPS, Top 10k .se,HTTPS,Rand 100k .se,HTTPS,Municipal .se,HTTPS},
